Generative Dynamics of Supreme Court Citations: Analysis with a New Statistical Network Model

### 2020-08-17 Tex/PA_rr/main.tex
fixed clashes with PA class
Original main.tex had settings that clashed with the PA class. These were ignored by overleaf but miktex (20.6) was not happy.
New Plots using only simulated annealing
updated description of results figures

\documentclass{cup-pan}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{geometry}

@@

\subsection{c-ERGM Coefficient Estimates}
The estimates from the c-ERGM are presented in Figures \ref{SCC_results_1} and \ref{SCC_results_2}. In these figures we depict coefficient estimates and 95\% confidence intervals for all of the effects for all the variables we discussed in sections \ref{covariate_terms} and \ref{dependence_terms}. The coefficients in an ERGM family model can be interpreted in the same way as logistic regression coefficients---they give the change in the log odds of a tie from $i$ to $j$ given a one-unit increase in the respective variable. We first discuss the dependence effect estimates in Figure \ref{SCC_results_1}. A circle indicates that the estimate was significant at an $\alpha=0.05$ level, while and square translates to a p-value between $0.05$ and $0.1$. A triangle signals that the estimate for a given year was not significant at an $\alpha=0.1$ level. The panel showing the results of the reciprocity statistic does not provide estimates for every term. In these missing terms there were no two cases that cited each other, making the estimate of the reciprocity statistic term equivalent to $-\infty$. %For those years, the reciprocity term is included in the model, but the estimate of $-\infty$. 
A similar scenario is visible for the \textit{Overruled Cases} variable. In the time period from 1953-1956 no cases that have been overruled have been cited which results in a non-estimable effect.

We first discuss our findings regarding the dependence terms. In most of the years that it is estimable, the reciprocity effect is statistically significantly positive, and substantial in magnitude. In a typical year, the presence of a citation from case $i$ to case $j$ increases the log-odds of a citation from case $j$ to case $i$ by approximately 0.50. Both transitivity effects---different term transitivity, and gwesp---are estimated to be positive and statistically significant in every year, and are even greater in magnitude than the reciprocity effect. The log-odds of a citation from case $i$ to case $j$ increases by more than 2 if there is at least one third case, $k$ that is cited by $i$, and cites to $j$. Results regarding the popularity effect (i.e., gwidegree) are generally supportive of the hypothesis of a popularity effect in Supreme Court citations, as the gwidegree estimate is negative in every term. There are some terms for which the result is not statistically significant at conventional levels. The popularity effect looks to have grown substantially stronger after the 2000 term. Contrary to expectations, we find that the hub effect is negative. That is, each additional citation sent by a case reduces the likelihood that the case is cited. For every citation sent, the log-odds of any citation to a case decreases by approximately 0.025---a result that is statistically significant in each term.

@@

\begin{figure}[H]
\centering
\includegraphics[width=14cm ]{SCC_results_1.pdf}
\caption{ERGM results for the dependence terms. Circles indicate a p-value smaller than 0.05, squares a p-value between 0.05 and 0.1 and triangles a p-value greater than 0.1. }
 \label{SCC_results_1}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=14cm ]{SCC_results_2.pdf}
\caption{ERGM results for the covariate terms. Circles indicate a p-value smaller than 0.05, squares a p-value between 0.05 and 0.1 and triangles a p-value greater than 0.1.}
 \label{SCC_results_2}
\end{figure}

>>>>

\documentclass{cup-pan}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{bm}
%\usepackage{amssymb}
%\usepackage{amsmath}
%\usepackage{amsthm}
%\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

@@

\subsection{c-ERGM Coefficient Estimates}
The estimates from the c-ERGM are presented in Figures \ref{SCC_results_1} and \ref{SCC_results_2}. In these figures we depict coefficient estimates and 95\% confidence intervals for all of the effects for all the variables we discussed in sections \ref{covariate_terms} and \ref{dependence_terms}. The coefficients in an ERGM family model can be interpreted in the same way as logistic regression coefficients---they give the change in the log odds of a tie from $i$ to $j$ given a one-unit increase in the respective variable. In our figures, a circle indicates that the estimate was significant at an $\alpha=0.05$ level, while an square translates to a p-value between $0.05$ and $0.1$. A triangle signals that the estimate for a given year was not significant at an $\alpha=0.1$ level. In each panel, the background shading indicates different chief justice courts, with the two darker shades representing, respectively, the Warren (1954-1969) and Rehnquist (1987-2005) courts. Finally, note that the panels showing results of the reciprocity statistic and the \textit{Overruled Cases} variable do not provide estimates for every term. In these missing terms there were no two cases that cited each other or no overruled cases being cited, making the estimate of these terms equivalent to $-\infty$. %For those years, the reciprocity term is included in the model, but the estimate of $-\infty$.

We first discuss the dependence effect estimates in Figure \ref{SCC_results_1}. In most of the years that it is estimable, the reciprocity effect is statistically significantly positive, and substantial in magnitude. In a typical year, the presence of a citation from case $i$ to case $j$ increases the log-odds of a citation from case $j$ to case $i$ by approximately 0.50. Both transitivity effects---different term transitivity, and gwesp---are estimated to be positive and statistically significant in every year, and are even greater in magnitude than the reciprocity effect. The log-odds of a citation from case $i$ to case $j$ increases by more than 2 if there is at least one third case, $k$ that is cited by $i$, and cites to $j$. Results regarding the popularity effect (i.e., gwidegree) are generally supportive of the hypothesis of a popularity effect in Supreme Court citations, as the gwidegree estimate is negative in every term. There are some terms for which the result is not statistically significant at conventional levels. The popularity effect looks to have grown substantially stronger after the 2000 term. Contrary to expectations, we find that the hub effect is negative. That is, each additional citation sent by a case reduces the likelihood that the case is cited. For every citation sent, the log-odds of any citation to a case decreases by approximately 0.025---a result that is statistically significant in each term.

@@

\begin{figure}
\centering
\includegraphics[width=14cm ]{SCC_results_1.pdf}
\caption{ERGM results for the dependence terms. Circles indicate a p-value smaller than 0.05, squares a p-value between 0.05 and 0.1 and triangles a p-value greater than 0.1. Different chief justice terms are indicated by shading in the background; the two grey areas indicate the Warren and Rehnquist courts.}
 \label{SCC_results_1}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=14cm ]{SCC_results_2.pdf}
\caption{ERGM results for the covariate terms. Circles indicate a p-value smaller than 0.05, squares a p-value between 0.05 and 0.1 and triangles a p-value greater than 0.1. Different chief justice terms are indicated by shading in the background; the two grey areas indicate the Warren and Rehnquist courts.}
 \label{SCC_results_2}
\end{figure}
